---
title: "MethodsAnalysis"
author: "Timo Roettger"
date: "11/24/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load in data}

# load in packages
library(rstudioapi)
library(tidyverse)

# load in statcheck output
method <- read_csv2("../data/methods_review.csv")
links <- read_csv("data/hyperlinks_reviewed.csv")

df <- full_join(method, links)

```

## 1. Number of Empirical and Experimental

How many papers are in the dataframe?

```{r echo = FALSE, eval = FALSE}

length(unique(method$title))

```


How many are empirical in nature?

```{r echo = FALSE, eval = FALSE}

method_empirical <- method %>% 
  filter(empirical == "yes")

nrow(method_empirical)

```

How many are experimental in nature?

```{r echo = FALSE, eval = FALSE}

method_experimental <- method %>% 
  filter(type == "experimental")

no_experiment <- nrow(method_experimental)
no_experiment

```

Other types?

```{r echo = FALSE, eval = FALSE}

xtabs(~type, method)

```

## 2. Number of Replications

How many of the experimental studies mentioned the term replic*

```{r echo = FALSE, eval = FALSE}

method_experimental_replic <- method_experimental %>% 
  filter(replic == "yes")

no_replic <- nrow(method_experimental_replic)
no_replic

```

None of which qualifies as a direct replication.

## 2. Number of Power analysis

How many studies did a power analysis?

```{r echo = FALSE, eval = FALSE}

method_experimental_power <- method_experimental %>% 
  filter(power == "yes")

no_power <- nrow(method_experimental_power)
no_power

```

Which papers did a power analysis?

```{r echo = FALSE, eval = FALSE}

method_experimental_power$title

```

```{r echo = FALSE, eval = FALSE}



```

```{r echo = FALSE, eval = FALSE}



```

```{r echo = FALSE, eval = FALSE}



```

```{r echo = FALSE, eval = FALSE}



```

