---
title: "StatsErrorAnalysis"
author: "Timo Roettger"
date: "10/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

# load in packages
library(rstudioapi)
library(tidyverse)

# load in statcheck output
stats <- read_csv("../data/statcheck_out.csv")

# load all articles
load(file = "../data/articles.RData")

```

Which unique articles can be analyzed with statcheck?

```{r}

unique(stats$Source)

```
What is the proportion of analyzable articles?

```{r}

prop_articles <- length(unique(stats$Source)) / length(unique(articles$title))
prop_articles

```

Almost half of all articles are analyzable

## Error Analysis

How many statistical indices could be checked?

```{r }

no_checks <- nrow(stats)
no_checks

```

How many statistical errors are detected?

```{r }

stats_error <- stats %>% 
  filter(Error == "TRUE")

no_errors <- nrow(stats_error)
no_errors

```

How many statistical errors are detected that cross the alpha level (= Decision errors)?

```{r }

stats_error_dec <- stats_error %>% 
  filter(DecisionError == "TRUE")

no_decision_errors <- nrow(stats_error_dec)
no_decision_errors

```

Proportion of errors?

```{r }

prop_errors <- no_errors / no_checks
prop_errors

```

How many articles have at least one error?

```{r }

no_error_articles <- 
  length(
    unique(
     stats[stats$Error == "TRUE",]$Source
      )
    )

no_error_articles

```

Proportion of articles with an error relative to those that statcheck has evaluated?

```{r }

prop_error_article <- no_error_articles / prop_articles
prop_error_article

```

What's the size of the mismatch between reported and calculated p-value

```{r}

# calculate difference between reported and calculated p-value
difference <- stats_error$Reported.P.Value - stats_error$Computed

# is the reported p-value lower
p_better <- ifelse(difference < 0, 1, 0)

range(difference)

```





