---
title             : "Assessing transparency and rigour in Laboratory Phonology"
shorttitle        : "Assessing LabPhon"

author: 
  - name          : "Timo B. Roettger"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "timo.b.roettger@gmail.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Data Curation
      - Investigation
      - Project administration
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      - Visualization
      
  - name          : "Mathias Stoeber"
    affiliation   : "2"
    role:
      - Conceptualization
      - Methodology
      - Data Curation
      - Investigation
      - Project administration
      - Writing - Review & Editing
      - Visualization

affiliation:
  - id            : "1"
    institution   : "Universitetet i Oslo"
  - id            : "2"
    institution   : "Universität Osnabrück"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "method" "replication" "open data" "reproducibility" "preregistration"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

Labphon is awesome because
- read the original Pierrehumbert, J., Beckman, M. E., & Ladd, D. R. (2000). Conceptual foundations of phonology as a laboratory science. Phonological knowledge: Conceptual and empirical issues, 273-304.

From official editorial policies: 

"The journal *strongly encourages* authors to make all data associated with their submission openly available, according to the FAIR principles (Findable, Accessible, Interoperable, Reusable). This should be linked to from a Data Accessibility Statement within the submitted paper, which will be made public upon publication. If data is not being made available with the journal publication then ideally a statement from the author should be provided within the submission to explain why. Data obtained from other sources must be appropriately credited."

"If research includes the use of software code, statistical analysis or algorithms then we also *recommend* that authors upload the code into Code Ocean, where it will be hosted on an open, cloud-based computational reproducibility platform, providing researchers and developers with an easy way to share, validate and discover code published in academic journals."

replicability and reproducibility in quant sciences
- lack or replicability
- reasons:
  - lack of transparency
    - errors and bias
    - unclear value of evidence (--> power)
   - researcher degrees of freedoms not detectable
  - lack of direct replication
    - cannot ensure empirical robustness
    
Where does LabPhon stand?    

# Is LabPhon research open?
RESULTS

Nope, mostly not. That is unfortunate because difficult to evaluate evidence and spot errors.
also makes replications more difficult and burdens the system by resource waste.

Are there errors? RESULTS. Hell yeah, could be avoided by more transparency
Power analyses? In those studies that perform test hypotheses, they do never perfrom power analysis. Difficult to evaluate both positive and negative findings.

What can we do

- Share everything
- Preregister (so far nobody does)
- do and publish direct replications


## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
